Analysis of split plot design using MCMCglmm

### 2020-06-12 README.Rmd
Remove R CMD checks. Rely on Docker

[![Last-changedate](https://img.shields.io/badge/last%20change-`r gsub('-', '--', Sys.Date())`-brightgreen.svg)](https://github.com/adamhsparks/rice.awd.pests/commits/master) [![minimal R version](https://img.shields.io/badge/R%3E%3D-`r as.character(getRversion())`-brightgreen.svg)](https://cran.r-project.org/)
[![Licence](https://img.shields.io/github/license/mashape/apistatus.svg)](http://choosealicense.com/licenses/mit/) ![R-CMD-check](https://github.com/adamhsparks/rice_AWD_ShB_analysis/workflows/R-CMD-check/badge.svg)

>>>>

[![Last-changedate](https://img.shields.io/badge/last%20change-`r gsub('-', '--', Sys.Date())`-brightgreen.svg)](https://github.com/adamhsparks/rice.awd.pests/commits/master) [![minimal R version](https://img.shields.io/badge/R%3E%3D-`r as.character(getRversion())`-brightgreen.svg)](https://cran.r-project.org/) [![DOI](https://zenodo.org/badge/DOI/10.5281/zenodo.3889800.svg)](https://doi.org/10.5281/zenodo.3889800)
